Bow shocks, bow waves, and dust waves. IV. Bow shape statistics

### 2019-04-19 papers/Papers1234/sec-obs-intro.tex
Finish intro for Paper IV

In this paper, we investigate the shapes of stellar bow shocks by
calculating the distributions of planitude and alatude for different
classes of bow shock source.  The remainder of the paper is organized as follows: in \S~\ref{sec:mid-infrared-arcs} we present an analysis of the shapes of several hundred bowshock candidates associated with OB stars from the

>>>>

In this paper, we investigate the shapes of stellar bow shocks by
calculating the distributions of planitude and alatude for different
classes of bow shock source.  The remainder of the paper is organized
as follows. In \S~\ref{sec:mid-infrared-arcs} we present an analysis
of the shapes of several hundred bowshock candidates associated with
OB stars from the \SI{24}{\um} survey of \citet{Kobulnicky:2016a}.
Our algorithm for automatically fitting and tracing the shapes is
described in \S~\ref{sec:autom-trac-fitt}, together with our ``star
rating'' system for evaluating the fit quality, while in
\S~\ref{sec:ob-shapes} we locate the sources on the planitude--alatude
plane.  In \S~\ref{sec:corr-size} we study the correlations amongst
non-shape parameters of the bow shock sources, such as angular size
and stellar magnitude, while in \S~\ref{sec:corr-shape} we explore the
correlations these parameters and the planitude and alatude.  In
\S~\ref{sec:far-infrared-arcs} we compare with results for bow shocks
around cool luminous stars and in \S~\ref{sec:stat-emiss-line} we
compare with results for staionary emission line arcs in the Orion
Nebula.  In \S~\ref{sec:discussion} we discuss the implications of our
findings for physical models of bow shock formation in the different
classes of sources, and in \S~\ref{sec:conclusion} we summarise our
results.  Further details of the statistical tests that we have
applied are provided in Appendix~\ref{sec:distr-p-values}.

### 2019-04-19 papers/Papers1234/sec-standing-wave.tex
Get as far as describing the phi(Xi) relation
Lots of reorganizing of Paper IV
Finish intro for Paper IV

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]
  {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
  \caption{Plane-of-sky projections of perturbed bow shapes.  In all
    cases, the base bow shape is ancantoid with \(\xi = 0.8\),
    \(\beta = 0.005\) and the perturbation is the same as in the central
    panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
    \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
    inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
    color and thickness, see key) and for different fractional phases
    of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
    (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
    the spatial coordinates are normalized to the instantaneous
    projected apex radius \(R_0'\) at each phase, so the apex does not
    appear to move.}.
  \label{fig:perturb-xy-prime}
\end{figure*}

\section{Perturbed bows}
\label{sec:perturbed-bows}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]
  {figs/wave-R90-vs-Rc-A010-N10}
  \includegraphics[width=\linewidth]
  {figs/wave-R90-vs-Rc-A005-N20}
  \caption{Diagnostic diagram for perturbed shapes}
  \label{fig:perturb-Rc-R90}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

>>>>

\section{Discussion}
\label{sec:discussion}

@@

% \begin{figure*}
%   \centering
%   \includegraphics[width=\linewidth]
%   {figs/wave_xyprime-A005-N20-ancantoid-xi080-beta000500}
%   \caption{Plane-of-sky projections of perturbed bow shapes.  In all
%     cases, the base bow shape is ancantoid with \(\xi = 0.8\),
%     \(\beta = 0.005\) and the perturbation is the same as in the central
%     panel of Fig.~\ref{fig:perturb-shapes}, with amplitude
%     \(A = 0.05\) and wave number \(N = 2.0\). Results are shown for
%     inclination angles \(i = 0\) to \(i = 75^\circ\) (indicated by line
%     color and thickness, see key) and for different fractional phases
%     of the oscillation: (a)~\(\varphi = 0.0\), (b)~\(\varphi = 0.25\),
%     (c)~\(\varphi = 0.50\). Unlike in Fig.~\ref{fig:perturb-shapes},
%     the spatial coordinates are normalized to the instantaneous
%     projected apex radius \(R_0'\) at each phase, so the apex does not
%     appear to move.}.
%   \label{fig:perturb-xy-prime}
% \end{figure*}

\subsection{Perturbed bows}
\label{sec:perturbed-bows}

Instability of bow \citep{Blondin:1998a}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]
  {figs/wave-R90-vs-Rc-A020-N10}
  \includegraphics[width=\linewidth]
  {figs/wave-R90-vs-Rc-A010-N20}
  \caption{Diagnostic diagram for perturbed shapes}
  \label{fig:perturb-Rc-R90}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "obs-bowshocks"
%%% End:
